Staged Abstract Interpreters

### 2019-06-14 paper/50_stageabs.tex
revision note

@@

\paragraph{Selective Caching} It is observed that the two-fold co-inductive
caching is used for every recursive call of our abstract interpreter. But this
is not necessary and even very expensive when generating code for atomic
expressions such as literals or variables, as they always terminate. Borrowing
the idea from the partition in ANF \cite{Flanagan:1993:ECC:155090.155113}, we
may use a selective caching algorithm:

>>>>

\iffalse
Revision: Solving Practical Challenges.
theoretically, all the things should work nicely. Unfolding the interpreter over the AST.
But the generated code is blowed up. For example .... This should not affect the correctness, 
but poses burden on the MSP system (ie LMS) and the next stage compiler/runtime (ie, scalac and JVM).
1) LMS becomes slower since a large IR graph is contructed during the staging.
2) Scalac becomes slower when reading a such large source code.
JVM has certain limitation on the size of a single method.

TODO: can we formulate selective caching as a partially-static data law.
TODO: lambda lifting for if
\fi

@@

\paragraph{Selective Caching} It is observed that the two-fold co-inductive
caching is used for every recursive call of our abstract interpreter. But this
is not necessary and even very expensive when generating code for atomic
expressions such as literals or variables, as they always terminate. Borrowing
the idea from the partition of A-Normal Form \cite{Flanagan:1993:ECC:155090.155113},
we may use a selective caching algorithm:
